### 2018-04-20 Paper/jaccardbaetica.tex
add new pic distribution

The distribution of amphora stamps in different conventus can be seen in Fig. 2. The majority of stamps found are concentrated in Hispalis with ... stamps while Astigi and Corduba concentrated  respectivamently. Mostly workshops show a homogeneity of distribution except La Catria or bla bla that show a big amount of stamps.  
%explicar por qué: mayor intensifación en las excavaciones

>>>>

The distribution of amphora stamps in different conventus can be seen in Fig. \ref{frequency}. The majority of stamps found are concentrated in Hispalis with 574 stamps while Corduba and Astigi with 267 and 146 stamps respectively. Mostly workshops show a homogeneity on frequency of stamps except La Catria and Arva (both show 29 different stamps) that show a big amount of different stamps.  QUIZAS HABLAR DE LA IMPORTANCIA DE LA CATRIA Y ARVA

\begin{figure}[htp]
	\centering
\includegraphics[width=\linewidth]{figs/frequency}
\caption{Dendrogram obtained by Morisita-Horn algorithm of different amphora workshops in Baetica area. Colors are represented by areas divided into Hispalis (red), Astigi (green) and Corduba (blue)}
\label{frequency}
\end{figure} 
%explicar por qué: mayor intensifación en las excavaciones quizás en sevilla
